### 2023-09-04 paper/sec-dis-pseudodata.tex
Ton -> tonne (metric unit)

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$ 
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field,  providing charged-lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

@@

\paragraph{FASER$\nu$2.}
%
This is proposed 20-ton neutrino experiment located on the LOS
of the LHC neutrino beam to be installed in the FPF cavern.
%
It is based on the same technology as FASER$\nu$, and hence
relies on a emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
It would be sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.
%
Given that FASER$\nu$2 is based on the same detector technology
as its predecessor, the same performance in terms of reconstruction
of final-state kinematics can be assumed.

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in the LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
Here we focus on the former.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon 
 identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers 
 interleaved with tungsten plates, for a total mass of 5 tons and fiducial length of 50 cm.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.
 %
 No information on the expected performance of the AdvSND-far detector
 is available and hence no estimate of the systematic errors
 is carried out.

@@

 With an expected fiducial (active) mass of 10 tons (30 tons) and a length of 7 m, FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  while final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
 downstream in the FPF cavern.
 %
 Here we present  projections for this baseline design of the experiment, FLArE10,
 as well as for a potential larger variant based on a fiducial mass of 100 ton, which
 is known as FLArE100.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim5\%$ of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since the muon energy from a charged-current interaction would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ are taken to be the same.

@@

 Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the six
 detectors
considered, separated into electron neutrinos and antineutrinos
and muon neutrinos and antineutrinos.
%
As mentioned above, for FLArE we assume that muon neutrinos interacting
in its fiducial volume will be measured
by the FASER$\nu$2 spectrometer.
  %
These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the
requirement that the momentum transfer and the final-state invariant mass are restricted
to the DIS region,
\be
\label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
\ee
%
The numbers in parenthesis indicate the event rates corresponding to charm
production, assuming heavy flavour tagging capabilities.
%
In the case of the FLArE detector, we display results for two proposed options with fiducial
masses of 10 and 100 tons.
%
As opposed to the number of interacting neutrinos presented
in~\cite{Feng:2022inv}, we now account for the
detector acceptances listed in  Table~\ref{tab:FPF_experiments}.

>>>>

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$ 
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tonnes with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field,  providing charged-lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

@@

\paragraph{FASER$\nu$2.}
%
This is proposed 20-tonne neutrino experiment located on the LOS
of the LHC neutrino beam to be installed in the FPF cavern.
%
It is based on the same technology as FASER$\nu$, and hence
relies on a emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
It would be sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.
%
Given that FASER$\nu$2 is based on the same detector technology
as its predecessor, the same performance in terms of reconstruction
of final-state kinematics can be assumed.

 \paragraph{AdvSND.}
 %
 This proposed experiment consists actually on  two detectors, a far-detector to be installed
 at the FPF with a coverage in neutrino pseudorapidity of $7.2 \le \eta_\nu \le 8.4$
 (hence off-LOS, same as SND@LHC) and a near detector installed somewhere else in the LHC
 complex and covering the range $4 \le \eta_\nu \le 5$.
 %
Here we focus on the former.
 %
 It would be
 composed (from upstream to downstream) by a target region
 for  vertex reconstruction and electromagnetic energy measurement, followed  by a hadronic calorimeter, a  muon 
 identification system, and finally  a magnet enabling muon charge and momentum measurements.
 %
 The target region of the detector, where the neutrino interactions take place, is made of thin sensitive layers 
 interleaved with tungsten plates, for a total mass of 5 tonnes and fiducial length of 50 cm.
 %
 This detector configuration will be able to track muons with energy $E_\nu \gsim 20$ GeV
 within an acceptance of 100 mrad and provide information on the charge
 of the  outgoing muon thanks to its magnet.
 %
 The total energy of the hadronic final state will be measured
 in the hadronic calorimeter.
 %
 No information on the expected performance of the AdvSND-far detector
 is available and hence no estimate of the systematic errors
 is carried out.

@@

 With an expected fiducial (active) mass of 10 tonnes (30 tonnes) and a length of 7 m, FLArE will
 detect final-state electrons with energies $E_{e}\lsim 2~\rm{TeV}$ and
 scattering angles up to 0.5 mrad,  while final-state muons
 with $\theta_\mu \lsim 0.025$ will be recorded by FASER$\nu$2
 downstream in the FPF cavern.
 %
 Here we present  projections for this baseline design of the experiment, FLArE10,
 as well as for a potential larger variant based on a fiducial mass of 100 tonnes, which
 is known as FLArE100.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim5\%$ of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.
 %
 Since the muon energy from a charged-current interaction would be measured by FASER$\nu$2, the
 performance parameters for $E_\mu$ are taken to be the same.

@@

 Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the six
 detectors
considered, separated into electron neutrinos and antineutrinos
and muon neutrinos and antineutrinos.
%
As mentioned above, for FLArE we assume that muon neutrinos interacting
in its fiducial volume will be measured
by the FASER$\nu$2 spectrometer.
  %
These event yields are computed from Eq.~(\ref{eq:event_yields_calculation}) with the
requirement that the momentum transfer and the final-state invariant mass are restricted
to the DIS region,
\be
\label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
\ee
%
The numbers in parenthesis indicate the event rates corresponding to charm
production, assuming heavy flavour tagging capabilities.
%
In the case of the FLArE detector, we display results for two proposed options with fiducial
masses of 10 and 100 tonnes.
%
As opposed to the number of interacting neutrinos presented
in~\cite{Feng:2022inv}, we now account for the
detector acceptances listed in  Table~\ref{tab:FPF_experiments}.

### 2023-09-04 paper/sec-results.tex
revision completed
Ton -> tonne (metric unit)

We begin by presenting results for the Hessian profiling of
the PDF4LHC21 set.
%
This proton PDF set is a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets, CT18~\cite{Hou:2019efy},
MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}.
%
Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa}.
%
Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a conservative estimate
of  current uncertainties associated to our understanding of proton PDFs.
%
We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
and study the stability of the results with respect to variations in the profiling inputs.

@@

\paragraph{Experiment dependence.}
%
Together with those for FASER$\nu$2, we have also produced PDF impact projections for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider both the 10 ton and 100 ton variants.
%
Fig.~\ref{fig:FASERnu2_FLAre10} compares the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE10 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340k)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.

>>>>

We begin by presenting results for the Hessian profiling of
the PDF4LHC21 set.
%
This proton PDF set is a Monte Carlo combination~\cite{Watt:2012tq,Carrazza:2015hva} of three global PDF sets, CT18~\cite{Hou:2019efy},
MSHT20~\cite{Bailey:2020ooq}, and NNPDF3.1~\cite{NNPDF:2017mvq}.
%
Its Hessian representations are obtained by means of the reduction methodologies developed in~\cite{Gao:2013bia,Carrazza:2015aoa,Carrazza:2016htc}.
%
Being based on the combination of three modern global PDF fits, PDF4LHC21 provides a conservative estimate
of  current uncertainties associated to our understanding of proton PDFs.
%
We profile PDF4LHC21 with pseudodata from various LHC neutrino experiments,
and study the stability of the results with respect to variations in the profiling inputs.

@@

\paragraph{Experiment dependence.}
%
Together with those for FASER$\nu$2, we have also produced PDF impact projections for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider both the 10 tonne and 100 tonne variants.
%
Fig.~\ref{fig:FASERnu2_FLAre10} compares the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE10 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 260k, 28k, and 57k (340k)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 39k, 3.5k, and 7.7k (45k) in the charm-tagged case.

### 2023-09-04 paper/tables/detectors.tex
Fixed a few sentences where fiducial volume was given units of mass, used forms like 'fiducial volume corresponding to a X kg detector'
Ton -> tonne (metric unit)

%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Charge ID & Acceptance  & Performance \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell,E_h \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
&   &   \multirow{2}{*}{(1.1 ton)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
$\delta \theta_\ell \sim 0.06$ mrad        \\
&   &     &       &  reco $E_h$ \& charm ID   &      $\delta E_h \sim 30\%$     \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\ell,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell,E_h \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
  &   &     &       &  reco $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND-far}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\ell,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reco $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
 &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered,
   we indicate their neutrino pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos.
  %
  For FLArE, we assume that muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.
  %
  See the description of each experiment in the text for more details.
  %
  For our projections we assume that FASER$\nu$ and SND@LHC acquire data
  for the Run III period ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period ($\mathcal{L}=3$ ab$^{-1}$).
  %
  In the case of FLArE, we consider results both
  for 10 ton and 100 ton fiducial volume detectors.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

>>>>

%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Charge ID & Acceptance  & Performance \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$}  &  \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  &   \multirow{2}{*}{Tungsten}  & \multirow{3}{*}{muons}      &   $E_\ell,E_h \gsim 100$ GeV   &      $\delta E_\ell \sim 30\% $    \\
&   &   \multirow{2}{*}{(1.1 tonnes)}  &       &  $\tan \theta_\ell \lsim 0.025$   &
$\delta \theta_\ell \sim 0.06$ mrad        \\
&   &     &       &  reco $E_h$ \& charm ID   &      $\delta E_h \sim 30\%$     \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\ell,E_h \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
  &    &  (0.83 tonnes)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $\eta_\nu \ge 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell,E_h \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 tonnes)}   &       &  $\tan \theta_\ell \lsim 0.05$   &   $\delta \theta_\ell \sim 0.06$ mrad      \\
  &   &     &       &  reco $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND-far}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\ell,E_h \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 tonnes)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reco $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE ({\bf *})}  & \multirow{3}{*}{$\eta_\nu \ge 7.5$} & \multirow{2}{*}{LAr}  & \multirow{3}{*}{muons}  &  $E_\ell,E_h \gsim 2$ GeV, $E_e \lsim 2$ TeV    &    $\delta E_e \sim 5\% $,  $\delta E_\mu \sim 30\% $ \\
&   &  \multirow{2}{*}{(10,~100~tonnes)}   &   & $\theta_\mu \lsim 0.025$, $\theta_e \lsim 0.5$ &    $\delta \theta_\ell \sim 15 $ mrad\\
 &   &     &  & reco $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered,
   we indicate their neutrino pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos.
  %
  For FLArE, we assume that muons would be measured in the FASER2 spectrometer
  situated downstream in the FPF cavern.
  %
  See the description of each experiment in the text for more details.
  %
  For our projections we assume that FASER$\nu$ and SND@LHC acquire data
  for the Run III period ($\mathcal{L}=150$ fb$^{-1}$), while FASER$\nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period ($\mathcal{L}=3$ ab$^{-1}$).
  %
  In the case of FLArE, we consider projections for fiducial volumes corresponding to both 10 and 100 tonne detectors.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------
